The Iterative Signature Algorithm for Gene Expression Data

### 2011-10-18 eisa/inst/doc/EISA_biclust.Rnw
eisa: added 'annotate' function, from the BioC SVN. This is a better way to convert Biclust objects.

Now we will convert the \Rclass{Biclust} object to an \Rclass{ISAModules} 
object, that is used in the \Rpackage{eisa} package. To help
some \Rpackage{eisa} functions, we add the name of the annotation package to 
the parameters stored in the \Rclass{Biclust} object, this is always advised.
The procedure makes use of the probe and sample names that are kept and stored 
in the \Rclass{Biclust} object, this information will be used later, e.g. for 
the enrichment analysis. The conversion itself can be performed with
the usual \Rfunction{as} function. 
<<convert bc to isa>>=
Bc@Parameters$annotation <- annotation(ALL.filtered)
modules <- as(Bc, "ISAModules")
modules
@

>>>>

Now we will convert the \Rclass{Biclust} object to an \Rclass{ISAModules} 
object, that is used in the \Rpackage{eisa} package. To help
some \Rpackage{eisa} functions, we add some biological annotation to
the \Rclass{Biclust} object.  of the annotation package to 
the parameters stored in the \Rclass{Biclust} object, this is always advised.
The procedure makes use of the probe and sample names that are kept and stored 
in the \Rclass{Biclust} object, this information will be used later, e.g. for 
the enrichment analysis. The conversion itself can be performed with
the usual \Rfunction{as} function. 
<<convert bc to isa>>=
Bc <- annotate(Bc, ALL.filtered)
modules <- as(Bc, "ISAModules")
modules
@

### 2011-10-18 eisa/inst/doc/EISA_tutorial.Rnw
eisa: tutorial updated, it failed on R 2.12.0 (beta).
eisa: added 'annotate' function, from the BioC SVN. This is a better way to convert Biclust objects.

You can use the \Rpackage{GO.db} package to obtain more information
about the enriched GO categories.
<<GO info,cache=FALSE>>=
sigCategories(GO$BP)[[1]]
library(GO.db)
mget(sigCategories(GO$BP)[[1]][1:3], GOTERM)
@

@@

\begin{figure}
<<conditions-plots-dysreg-real,fig=TRUE,width=10,height=8,echo=FALSE,results=hide>>=
<<conditions-plots-dysreg>>
@
\caption{Condition plots for the best separator module found with
  random seeds and the one found with the smart seeds. They are
  essentially the same, with some minor differences. 
}
\label{fig:dysregmodules}
\end{figure}

@@

\begin{figure}
\centering
<<B1-cond-plots-real,fig=TRUE,echo=FALSE,results=hide,width=10,height=8>>=
<<B1-cond-plots>>
@ 
\caption{Condition plots for the modules that best separate the B1-type 
  ALL samples from the other B-cell ALL samples. The two modules are essentially
  the same.}
\label{fig:B1condplots}
\end{figure}

>>>>

You can use the \Rpackage{GO.db} package to obtain more information
about the enriched GO categories.
<<GO info,cache=FALSE>>=
sigCategories(GO$BP)[[1]]
library(GO.db)
mget(na.omit(sigCategories(GO$BP)[[1]][1:3]), GOTERM)
@

@@

<<conditions-plots-dysreg-real,width=10,height=8,echo=FALSE,results=hide>>=
png("cond-dysreg.png", width=800, height=400)
<<conditions-plots-dysreg>>
dev.off()
@

\begin{figure}
\includegraphics[width=\textwidth]{cond-dysreg.png}
\caption{Condition plots for the best separator module found with
  random seeds and the one found with the smart seeds. They are
  essentially the same, with some minor differences. 
}
\label{fig:dysregmodules}
\end{figure}

@@

<<B1-cond-plots-real,echo=FALSE,results=hide,width=10,height=8>>=
png("cond-dysreg2.png", width=800, height=400)
<<B1-cond-plots>>
dev.off()
@ 
\begin{figure}
\centering
\includegraphics[width=\textwidth]{cond-dysreg2.png}
\caption{Condition plots for the modules that best separate the B1-type 
  ALL samples from the other B-cell ALL samples. The two modules are essentially
  the same.}
\label{fig:B1condplots}
\end{figure}
